Project1_RM_Objective_1

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.2.16.20.Rmd
Add files via upload

linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(linear.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.intuitive.final.model)^2))
summary(linear.intuitive.final.model)
par(mfrow=c(2,2))
plot(linear.intuitive.final.model)
confint(linear.intuitive.final.model)
```

@@

log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(log.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(log.intuitive.final.model)^2))
summary(log.intuitive.final.model)
par(mfrow=c(2,2))
plot(log.intuitive.final.model)
confint(log.intuitive.final.model)
```

@@

linear.forward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.forward.final.model))
print("Full Model BIC: ")
print(BIC(linear.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.forward.final.model)^2))
summary(linear.forward.final.model)
par(mfrow=c(2,2))
plot(linear.forward.final.model)
```

@@

log.forward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.forward.final.model))
print("Full Model BIC: ")
print(BIC(log.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.forward.final.model)^2))
summary(log.forward.final.model)
par(mfrow=c(2,2))
plot(log.forward.final.model)
```

@@

linear.backward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.backward.final.model))
print("Full Model BIC: ")
print(BIC(linear.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.backward.final.model)^2))
summary(linear.backward.final.model)
par(mfrow=c(2,2))
plot(linear.backward.final.model)
```

@@

log.backward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.backward.final.model))
print("Full Model BIC: ")
print(BIC(log.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.backward.final.model)^2))
summary(log.backward.final.model)
par(mfrow=c(2,2))
plot(log.backward.final.model)
```

@@

linear.seqrep.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(linear.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.seqrep.final.model)^2))
summary(linear.seqrep.final.model)
par(mfrow=c(2,2))
plot(linear.seqrep.final.model)
```

@@

log.seqrep.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(log.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(log.seqrep.final.model)^2))
summary(log.seqrep.final.model)
par(mfrow=c(2,2))
plot(log.seqrep.final.model)
```

>>>>

linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(linear.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.intuitive.final.model)^2))
summary(linear.intuitive.final.model)
par(mfrow=c(2,2))
plot(linear.intuitive.final.model)
vif(linear.intuitive.final.model)
confint(linear.intuitive.final.model)
```

@@

log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(log.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(log.intuitive.final.model)^2))
summary(log.intuitive.final.model)
par(mfrow=c(2,2))
plot(log.intuitive.final.model)
vif(log.intuitive.final.model)
confint(log.intuitive.final.model)
```

@@

linear.forward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.forward.final.model))
print("Full Model BIC: ")
print(BIC(linear.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.forward.final.model)^2))
summary(linear.forward.final.model)
par(mfrow=c(2,2))
plot(linear.forward.final.model)
vif(linear.forward.final.model)
confint(linear.forward.final.model)
```

@@

log.forward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.forward.final.model))
print("Full Model BIC: ")
print(BIC(log.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.forward.final.model)^2))
summary(log.forward.final.model)
par(mfrow=c(2,2))
plot(log.forward.final.model)
vif(log.forward.final.model)
confint(log.forward.final.model)
```

@@

linear.backward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.backward.final.model))
print("Full Model BIC: ")
print(BIC(linear.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.backward.final.model)^2))
summary(linear.backward.final.model)
par(mfrow=c(2,2))
plot(linear.backward.final.model)
vif(linear.backward.final.model)
confint(linear.backward.final.model)
```

@@

log.backward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.backward.final.model))
print("Full Model BIC: ")
print(BIC(log.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.backward.final.model)^2))
summary(log.backward.final.model)
par(mfrow=c(2,2))
plot(log.backward.final.model)
vif(log.backward.final.model)
confint(log.backward.final.model)
```

@@

linear.seqrep.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(linear.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.seqrep.final.model)^2))
summary(linear.seqrep.final.model)
par(mfrow=c(2,2))
plot(linear.seqrep.final.model)
vif(linear.seqrep.final.model)
confint(linear.seqrep.final.model)
```

@@

log.seqrep.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(log.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(log.seqrep.final.model)^2))
summary(log.seqrep.final.model)
par(mfrow=c(2,2))
plot(log.seqrep.final.model)
vif(log.seqrep.final.model)
confint(log.seqrep.final.model)
```
